---
title: "mingroups_2_preprocessing"
author: "Youssef Amin"
date: "2024-05-01"
output: html_document
---
Load necessary packages
```{r setup, include=FALSE}
library(ggplot2)
library(car)
library(dplyr)
library(sjPlot)
library(haven)
library(tidyverse)
library(psych)
library(lme4)
library(magrittr)
library(BayesFactor)
library(bayestestR)
```

Set working directory to the location of the current file.
```{r}
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

Turn off scientific notation.
```{r}
options(scipen = 999)
```

# note on the data: 
# for the condition variable, 0 = underestimator; 1 = overestimator

Read in datasets and remove test (non-prolific) runs
```{r}
groups2 <- read.csv('/Users/youssefamin/Dropbox/MinimalGroup_NHB_Master/MinimalGroup_NHB2/data/nhb2_raw_data.csv')
groups1 <- read.csv('/Users/youssefamin/Dropbox/MinimalGroup_NHB_Master/MinimalGroup_NHB1/data/nhb1_bothsamples_processed.csv')

#Remove any repeat Prolific PID, IP addresses from earlier studies
##Prolific IDs
duplicate_pids <- intersect(groups1$PROLIFIC_PID, groups2$PROLIFIC_PID)

# Remove rows from groups2 with duplicate PROLIFIC_PID
groups2 <- groups2[!groups2$PROLIFIC_PID %in% duplicate_pids, ]

##IP Addresses
duplicate_ips <- intersect(groups1$IPAddress, groups2$IPAddress)

# Remove rows from groups2 with duplicate IPAddress
groups2 <- groups2[!groups2$IPAddress %in% duplicate_ips, ] #5 repeat IP addresses from study 1 957 -> 952

#Remove any repeat IP addresses within study 2
# Convert StartData to datetime format if it is not already
groups2$StartDate <- as.POSIXct(groups2$StartDate, format="%Y-%m-%d %H:%M:%S") 

# Sort data by IP address and StartData
groups2 <- groups2[order(groups2$IPAddress, groups2$StartDate), ]

# Identify duplicates based on IP address and keep only the first occurrence
groups2 <- groups2[!duplicated(groups2$IPAddress), ] #7 repeat IP addresses within this study 952 -> 945


###Remove non-prolific/test runs
groups2 %<>% filter(PROLIFIC_PID != "")
totalsamplesize <- nrow(groups2)

###Remove participants that didn't finish
groups2<-groups2 %>% filter(Finished == "True" ) #945 -> 943
finishedsamplesize <- nrow(groups2)
```

Attention Checks
```{r}
# filter out participants who answered the attention check question incorrectly. 
groups2 <- groups2 %>%
  filter(skyColor == 'purple') #before: 943 , after: 928
samplesize_skyAttention <- nrow(groups2) #15 removed for sky attention check


# check whether people accurately assigned themselves to groups.

#Remove RANK columns, same info is contained in GROUP columns
groups2 %<>% dplyr::select(-c(AttCheckOrder1_0_1_RANK, 
                       AttCheckOrder1_1_1_RANK,
                       AttnCheckOrder2_0_1_RANK, 
                       AttnCheckOrder2_1_1_RANK))


# create variable which shows which people did which attention check
groups2 <- groups2 %>%
  mutate(Check1 = case_when(
    (nzchar(AttCheckOrder1_0_GROUP) | nzchar(AttCheckOrder1_1_GROUP)) ~ TRUE,
    TRUE ~ FALSE  # Default case to assign FALSE
  ))

groups2 <- groups2 %>%
  mutate(Check2 = case_when(
    (nzchar(AttnCheckOrder2_0_GROUP) | nzchar(AttnCheckOrder2_1_GROUP)) ~ TRUE,
    TRUE ~ FALSE  # Default case to assign FALSE
  ))


#note on the data, for attention check 1, find what attention check people did (1 or 2)
#For attention check 1, 0 was blue and 1 was green
#For attention check 2, 0 was green and blue was 1
##Rennaming columns to make code more intuitive
groups2 %<>%
  rename(Check1_ChoseBlue=AttCheckOrder1_0_GROUP, 
       Check1_ChoseGreen=AttCheckOrder1_1_GROUP,
       Check2_ChoseGreen = AttnCheckOrder2_0_GROUP,
       Check2_ChoseBlue = AttnCheckOrder2_1_GROUP)


#Create assignment check column
groups2 <- groups2 %>%
  mutate(
    # Transform these columns to TRUE if they contain data, otherwise FALSE
    Check1_ChoseBlue = nzchar(Check1_ChoseBlue),
    Check2_ChoseBlue = nzchar(Check2_ChoseBlue),
    Check1_ChoseGreen = nzchar(Check1_ChoseGreen),
    Check2_ChoseGreen = nzchar(Check2_ChoseGreen)
  ) %>%
  mutate(
    # Create 'AssignmentCheck' based on the new boolean columns
    AssignmentCheck = case_when(
      ingroup == 'blue' & (Check1_ChoseBlue | Check2_ChoseBlue) ~ TRUE,
      ingroup == 'green' & (Check1_ChoseGreen | Check2_ChoseGreen) ~ TRUE,
      TRUE ~ FALSE  # Default to FALSE if none of the conditions are met
    )
  )


##Remove those who assigned themselves to the wrong group
groups2 %<>% filter(AssignmentCheck == TRUE) #before 928 #after: 913
processed_samplesize <- nrow(groups2) #15 removed in assignment check
```


Cleaning up demographic data
```{r}
####Age####
describe(as.numeric(groups2$dem_Age)) #AGE: M = 45.28 ,  SD = 15.27 ; 
is.na(as.numeric(groups2$dem_Age)) %>% sum() #How many people didn't respond, none
(as.numeric(groups2$dem_Age) < 18 )%>% sum(na.rm=T) #How many people said they were under 18, none
groups2 %<>% filter(as.numeric(dem_Age) >= 18)##Remove people who left age blank or who reported they were under 18, none


####Gender####
table(groups2$dem_Sex) #so many different responses that I added them up myself, as there is no way to soft code this, there will always be varying type-ins
sum(1, 1, 14, 249, 13, 2, 173, 1, 4, 1, 1, 3, 3, 1, 1) + #468 Cis Women/Female
sum(1, 1, 3, 5, 2, 228, 192, 3) + #435 Male
sum(1,3) + #4 Non-binary
sum(1,1,1,1,2) #6 Other

####Education####
table(groups2$dem_Education)
groups2$dem_Education.n<-dplyr::recode(groups2$dem_Education,
                                       "2-year College Degree" = 4,
                                       "4-year College Degree" = 5,
                                       "Doctoral Degree" = 7,
                                       "High School / GED" = 2,
                                       "Less than High School" = 1,
                                       "Masters Degree" = 6,
                                       "Professional Degree (JD, MD)" = 7,
                                       "Some College" = 3)
# Reorder Education levels
groups2$dem_Education <- factor(groups2$dem_Education, 
                                 levels = c("Less than High School", "High School / GED", "Some College", 
                                            "2-year College Degree", "4-year College Degree", 
                                            "Masters Degree", "Professional Degree (JD, MD)", 
                                            "Doctoral Degree"))

median(groups2$dem_Education.n, na.rm = T) #5, half of our participants had a four year college degree or higher



####Income####
table(groups2$dem_Income)
groups2$dem_Income.n<-dplyr::recode(groups2$dem_Income,
                                       "Less than $30,000" = 1,
                                       "$30,000 – $39,999" = 2,
                                       "$40,000 – $49,999" = 3,
                                       "$50,000 – $59,999" = 4,
                                       "$60,000 – $69,999" = 5,
                                       "$70,000 – $79,999" = 6,
                                       "$80,000 – $89,999" = 7,
                                       "$90,000 – $99,999" = 8,
                                       "$100,000 or more" = 9,
                                       .default = NA_real_)

median(groups2$dem_Income.n, na.rm = T) #Median income of 70,000 - 79,999

groups2$dem_BasicRace <- dplyr::recode(groups2$dem_Race,
              "White" = "White",
              "Asian" = "Asian",
              "Black or African American" = "Black",
              "American Indian or Alaskan Native" = "American Indian or Alaskan Native",
              "Native Hawaiian or Other Pacific Islander" = "Native Hawaiian or Other Pacific Islander",
              .default = "Other or Mixed")


#use this code to see who reported no age: which(groups2$dem_Age == "")
```


###############################,
###############################,
# CALCULATE POLITICAL IDEOLOGY // EXTREMITY
###############################,
###############################,

```{r}
###############,
##  SECS Scale
###############,

#Replace any missing SEC values with 50
groups2$SECS_1<-case_when(groups2$SECS_1 == "" ~ '50',
                          TRUE ~ as.character(groups2$SECS_1))
groups2$SECS_2<-case_when(groups2$SECS_2 == "" ~ '50',
                          TRUE ~ as.character(groups2$SECS_2))
groups2$SECS_3<-case_when(groups2$SECS_3 == "" ~ '50',
                          TRUE ~ as.character(groups2$SECS_3))
groups2$SECS_4<-case_when(groups2$SECS_4 == "" ~ '50',
                          TRUE ~ as.character(groups2$SECS_4))
groups2$SECS_5<-case_when(groups2$SECS_5 == "" ~ '50',
                          TRUE ~ as.character(groups2$SECS_5))
groups2$SECS_6<-case_when(groups2$SECS_6 == "" ~ '50',
                          TRUE ~ as.character(groups2$SECS_6))
groups2$SECS_7<-case_when(groups2$SECS_7 == "" ~ '50',
                          TRUE ~ as.character(groups2$SECS_7))
groups2$SECS_8<-case_when(groups2$SECS_8 == "" ~ '50',
                          TRUE ~ as.character(groups2$SECS_8))
groups2$SECS_9<-case_when(groups2$SECS_9 == "" ~ '50',
                          TRUE ~ as.character(groups2$SECS_9))
groups2$SECS_10<-case_when(groups2$SECS_10 == "" ~ '50',
                          TRUE ~ as.character(groups2$SECS_10))

# recode the SECS items so that higher scores = more conservative. 
groups2 <- groups2 %>%
  mutate(RC_SECS_1 = 100 - as.numeric(SECS_1),
         RC_SECS_5 = 100 - as.numeric(SECS_5))


# calculate mean SECs Scores. 
groups2 <- groups2 %>%
  rowwise() %>%
  mutate(mean_SECS = mean(c(RC_SECS_1,as.numeric(SECS_2),as.numeric(SECS_3),
                            as.numeric(SECS_4),as.numeric(RC_SECS_5),as.numeric(SECS_6),
                            as.numeric(SECS_7),as.numeric(SECS_8),as.numeric(SECS_9),
                            as.numeric(SECS_10),as.numeric(SECS_11),as.numeric(SECS_12), na.rm = T))) %>%
  ungroup()

#scaled to 1-9
groups2$SECS_scaled<-((groups2$mean_SECS-min(groups2$mean_SECS,na.rm=T))*(9-1)/(max(groups2$mean_SECS,na.rm=T)-min(groups2$mean_SECS,na.rm = T)))+1

###############,
##  CREATE COMPOSITE MEASURE
###############,
groups2$EconOrient<-case_when(groups2$EconOrient=='Extremely Liberal\n1\n' ~ 1,
          groups2$EconOrient=="2" ~ 2,
          groups2$EconOrient=='3'~3,
          groups2$EconOrient=='4'~4,
          groups2$EconOrient=="Moderate\n5\n" ~ 5,
          groups2$EconOrient=="6" ~ 6,
          groups2$EconOrient=="7"~7,
          groups2$EconOrient=="8"~8,
          groups2$EconOrient=="Extremely Conservative\n9\n" ~ 9,
          groups2$EconOrient==''~NA_real_)

#Make SocOrient Numeric
groups2$SocOrient<-case_when(groups2$SocOrient=='Extremely Liberal\n1\n' ~ 1,
                              groups2$SocOrient=="2" ~ 2,
                              groups2$SocOrient=='3'~3,
                              groups2$SocOrient=='4'~4,
                              groups2$SocOrient=="Moderate\n5\n" ~ 5,
                              groups2$SocOrient=="6" ~ 6,
                              groups2$SocOrient=="7"~7,
                              groups2$SocOrient=="8"~8,
                              groups2$SocOrient=="Extremely Conservative\n9\n" ~ 9,
                              groups2$SocOrient==''~NA_real_)

#Make PolOrient Numeric
groups2$PolOrient<-case_when(groups2$PolOrient=='Extremely Liberal\n1\n' ~ 1,
                             groups2$PolOrient=="2" ~ 2,
                             groups2$PolOrient=='3'~3,
                             groups2$PolOrient=='4'~4,
                             groups2$PolOrient=="Moderate\n5\n" ~ 5,
                             groups2$PolOrient=="6" ~ 6,
                             groups2$PolOrient=="7"~7,
                             groups2$PolOrient=="8"~8,
                             groups2$PolOrient=="Extremely Conservative\n9\n" ~ 9,
                             groups2$PolOrient==''~NA_real_)

# standardize the four political orientation variables
groups2 <- groups2 %>%
  mutate(z_mean_SECS = scale(mean_SECS),
         z_PolOrient = scale(PolOrient),
         z_EconOrient = scale(EconOrient),
         z_SocOrient = scale(SocOrient))

# create standardized political orientation variable. 
groups2 <- groups2 %>%
  rowwise() %>%
  mutate(composite_political_orientation = mean(c(z_mean_SECS, z_PolOrient,z_EconOrient,z_SocOrient), na.rm = T),
         self_identification_political = mean(c(z_PolOrient,z_EconOrient,z_SocOrient), na.rm = T)) %>%
  ungroup() %>% 
  mutate(composite_political_orientation_z = scale(composite_political_orientation),
         self_identification_political_z = scale(self_identification_political))


#raw political orientation
groups2 <- groups2 %>%
  rowwise() %>%
  mutate(composite_political_orientation.raw = mean(c(SECS_scaled, PolOrient,EconOrient,SocOrient), na.rm = T)) %>%
  ungroup() #scaled 1-9


###############################,
###############################,
# CALCULATE IDEOLOGICAL EXTREMITY
###############################,
###############################,

# calculate ideological extremity by recoding to look at the distance from the participant's  
# score to the midpoint of the scale.
groups2 <- groups2 %>%
  mutate(PolOrientExtremity = abs(5 - PolOrient),
         SocOrientExtremity = abs(5 - SocOrient),
         EconOrientExtremity = abs(5 - EconOrient),
         SECSExtremity = abs(5 - SECS_scaled))

# standardize extremity variables.
groups2 <- groups2 %>%
  mutate(z_PolOrientExtremity = scale(PolOrientExtremity),
         z_SocOrientExtremity = scale(SocOrientExtremity),
         z_EconOrientExtremity = scale(EconOrientExtremity),
         z_SECSExtremity = scale(SECSExtremity)) %>%
  ungroup()

# calculate mean ideological extremity
groups2 <- groups2 %>%
  rowwise() %>%
  mutate(composite_ideological_extremity = mean(c(z_PolOrientExtremity,z_SocOrientExtremity, z_EconOrientExtremity,z_SECSExtremity), na.rm = T),
         selfIDExtremity = mean(c(z_PolOrientExtremity,z_SocOrientExtremity, z_EconOrientExtremity))) %>%
  ungroup() %>% 
  mutate(composite_ideological_extremity_z = scale(composite_ideological_extremity),
         selfIDExtremity_z = scale(selfIDExtremity))


#raw
groups2 <- groups2 %>%
  rowwise() %>%
  mutate(composite_ideological_extremity.raw = mean(c(PolOrientExtremity,SocOrientExtremity,EconOrientExtremity,SECSExtremity), na.rm = T)) %>%
  ungroup()
```



##########################################,
##########################################,
##  CALCULATE DEPENDENT VARIABLES ########
##########################################,
##########################################,
```{r}
#########################,
# IDENTIFICATION MEASURES
#########################,

##Making Ingroup Identification Numeric
groups2$IngroupIdentify<-case_when(
  groups2$IngroupIdentify == "Strongly Disagree\n1\n" ~ 1,
  groups2$IngroupIdentify == "2" ~ 2,
  groups2$IngroupIdentify == "3" ~ 3,
  groups2$IngroupIdentify == "4" ~ 4,
  groups2$IngroupIdentify == "5" ~ 5,
  groups2$IngroupIdentify == "6" ~ 6,
  groups2$IngroupIdentify == "Strongly Agree\n7\n" ~ 7
)

##Making Outgroup Identification Numeric
groups2$OutgroupIdentify<-case_when(
  groups2$OutgroupIdentify == "Strongly Disagree\n1\n" ~ 1,
  groups2$OutgroupIdentify == "2" ~ 2,
  groups2$OutgroupIdentify == "3" ~ 3,
  groups2$OutgroupIdentify == "4" ~ 4,
  groups2$OutgroupIdentify == "5" ~ 5,
  groups2$OutgroupIdentify == "6" ~ 6,
  groups2$OutgroupIdentify == "Strongly Agree\n7\n" ~ 7
)

#scale
groups2$z_IngroupIdentify<-scale(groups2$IngroupIdentify)

# calculate difference between ingroup and outgroup identification. 
groups2 <- groups2 %>%
  mutate(ingroup_minus_outgroup_identify = IngroupIdentify - OutgroupIdentify,
         z_ingroup_minus_outgroup_identify = scale(ingroup_minus_outgroup_identify))


#########################,
# EVALUATIVE TRAIT RATINGS
#########################,
#Recoding the Ingroup Trait Evaluation to Numeric
groups2$InTraits_1<-dplyr::recode(groups2$InTraits_1, 
                        "Not at all\n1\n" = 1,
                        "2" = 2,
                        "3" = 3,
                        "4" = 4,
                        "5" = 5,
                        "6" = 6,
                        "Very much\n7\n" = 7)
groups2$InTraits_2<-dplyr::recode(groups2$InTraits_2, 
                        "Not at all\n1\n" = 1,
                        "2" = 2,
                        "3" = 3,
                        "4" = 4,
                        "5" = 5,
                        "6" = 6,
                        "Very much\n7\n" = 7)
groups2$InTraits_3<-dplyr::recode(groups2$InTraits_3, 
                        "Not at all\n1\n" = 1,
                        "2" = 2,
                        "3" = 3,
                        "4" = 4,
                        "5" = 5,
                        "6" = 6,
                        "Very much\n7\n" = 7)
groups2$InTraits_4<-dplyr::recode(groups2$InTraits_4, 
                        "Not at all\n1\n" = 1,
                        "2" = 2,
                        "3" = 3,
                        "4" = 4,
                        "5" = 5,
                        "6" = 6,
                        "Very much\n7\n" = 7)
groups2$InTraits_5<-dplyr::recode(groups2$InTraits_5, 
                        "Not at all\n1\n" = 1,
                        "2" = 2,
                        "3" = 3,
                        "4" = 4,
                        "5" = 5,
                        "6" = 6,
                        "Very much\n7\n" = 7)
groups2$InTraits_6<-dplyr::recode(groups2$InTraits_6, 
                        "Not at all\n1\n" = 1,
                        "2" = 2,
                        "3" = 3,
                        "4" = 4,
                        "5" = 5,
                        "6" = 6,
                        "Very much\n7\n" = 7)

#Recoding the Outgroup Trait Evaluation to Numeric
groups2$OutTraits_1<-dplyr::recode(groups2$OutTraits_1, 
                         "Not at all\n1\n" = 1,
                         "2" = 2,
                         "3" = 3,
                         "4" = 4,
                         "5" = 5,
                         "6" = 6,
                         "Very much\n7" = 7)
groups2$OutTraits_2<-dplyr::recode(groups2$OutTraits_2, 
                         "Not at all\n1\n" = 1,
                         "2" = 2,
                         "3" = 3,
                         "4" = 4,
                         "5" = 5,
                         "6" = 6,
                         "Very much\n7" = 7)
groups2$OutTraits_3<-dplyr::recode(groups2$OutTraits_3, 
                         "Not at all\n1\n" = 1,
                         "2" = 2,
                         "3" = 3,
                         "4" = 4,
                         "5" = 5,
                         "6" = 6,
                         "Very much\n7" = 7)
groups2$OutTraits_4<-dplyr::recode(groups2$OutTraits_4, 
                         "Not at all\n1\n" = 1,
                         "2" = 2,
                         "3" = 3,
                         "4" = 4,
                         "5" = 5,
                         "6" = 6,
                         "Very much\n7" = 7)
groups2$OutTraits_5<-dplyr::recode(groups2$OutTraits_5, 
                         "Not at all\n1\n" = 1,
                         "2" = 2,
                         "3" = 3,
                         "4" = 4,
                         "5" = 5,
                         "6" = 6,
                         "Very much\n7" = 7)
groups2$OutTraits_6<-dplyr::recode(groups2$OutTraits_6, 
                         "Not at all\n1\n" = 1,
                         "2" = 2,
                         "3" = 3,
                         "4" = 4,
                         "5" = 5,
                         "6" = 6,
                         "Very much\n7" = 7)

# recode negative trait ratings so that higher scores = more positive evaluations
groups2 <- groups2 %>%
  mutate(RC_InTraits_1 = 8 - InTraits_1,
         RC_InTraits_4 = 8 - InTraits_4,
         RC_InTraits_6 = 8 - InTraits_6,
         RC_OutTraits_1 = 8 - OutTraits_1,
         RC_OutTraits_4 = 8 - OutTraits_4,
         RC_OutTraits_6 = 8 - OutTraits_6)

# calculate mean evaluative trait ratings for ingroups and outgroups, such that higher scores = more positive evaluations. 
groups2 <- groups2 %>%
  rowwise() %>%
  mutate(mean_ingroup_traits_positive = mean(c(RC_InTraits_1,InTraits_2,InTraits_3,
                                               RC_InTraits_4,InTraits_5,RC_InTraits_6))) %>%
  mutate(mean_outgroup_traits_positive = mean(c(RC_OutTraits_1,OutTraits_2,OutTraits_3,
                                               RC_OutTraits_4,OutTraits_5,RC_OutTraits_6))) %>%
  ungroup()

# calculate the difference score between positivity of ingroup trait ratings and outgroups trait ratings.
groups2 <- groups2 %>%
  mutate(ingroup_minus_outgroup_traits_positive = mean_ingroup_traits_positive - mean_outgroup_traits_positive,
         z_ingroup_minus_outgroup_traits_positive = scale(ingroup_minus_outgroup_traits_positive))



#######################,
### TAJFEL MATRICES
#######################,

# first recode the tajfel matrices to count up the number 
# of points awarded to the ingroup and to the outgroup.

# Matrix 1: FAV vs. MJP OPPOSED
groups2 <- groups2 %>%
  mutate(MatrixA_O_ingroup_points = case_when(
    MatrixA_O == "A" ~ 19,
    MatrixA_O == "B" ~ 18,
    MatrixA_O == "C" ~ 17,
    MatrixA_O == "D" ~ 16,
    MatrixA_O == "E" ~ 15,
    MatrixA_O == "F" ~ 14,
    MatrixA_O == "G" ~ 13,
    MatrixA_O == "H" ~ 12,
    MatrixA_O == "I" ~ 11,
    MatrixA_O == "J" ~ 10,
    MatrixA_O == "K" ~ 9,
    MatrixA_O == "L" ~ 8,
    MatrixA_O == "M" ~ 7
  )) %>%
  mutate(MatrixA_O_outgroup_points = case_when(
    MatrixA_O == "A" ~ 1,
    MatrixA_O == "B" ~ 3,
    MatrixA_O == "C" ~ 5,
    MatrixA_O == "D" ~ 7,
    MatrixA_O == "E" ~ 9,
    MatrixA_O == "F" ~ 11,
    MatrixA_O == "G" ~ 13,
    MatrixA_O == "H" ~ 15,
    MatrixA_O == "I" ~ 17,
    MatrixA_O == "J" ~ 19,
    MatrixA_O == "K" ~ 21,
    MatrixA_O == "L" ~ 23,
    MatrixA_O == "M"~ 25
  ))

# Matrix 2: FAV vs. MJP Together
groups2 <- groups2 %>%
  mutate(MatrixA_T_ingroup_points = case_when(
    MatrixA_T == "A" ~ 25,
    MatrixA_T == "B" ~ 23,
    MatrixA_T == "C" ~ 21,
    MatrixA_T == "D" ~ 19,
    MatrixA_T == "E" ~ 17,
    MatrixA_T == "F" ~ 15,
    MatrixA_T == "G" ~ 13,
    MatrixA_T == "H" ~ 11,
    MatrixA_T == "I" ~ 9,
    MatrixA_T == "J" ~ 7,
    MatrixA_T == "K" ~ 5,
    MatrixA_T == "L" ~ 3,
    MatrixA_T == "M"~ 1
  )) %>%
  mutate(MatrixA_T_outgroup_points = case_when(
    MatrixA_T == "A" ~ 7,
    MatrixA_T == "B" ~ 8,
    MatrixA_T == "C" ~ 9,
    MatrixA_T == "D" ~ 10,
    MatrixA_T == "E" ~ 11,
    MatrixA_T == "F" ~ 12,
    MatrixA_T == "G" ~ 13,
    MatrixA_T == "H" ~ 14,
    MatrixA_T == "I" ~ 15,
    MatrixA_T == "J" ~ 16,
    MatrixA_T == "K" ~ 17,
    MatrixA_T == "L" ~ 18,
    MatrixA_T == "M" ~ 19
  ))


# Matrix 3: MD vs. MIP+MJP opposed
groups2 <- groups2 %>%
  mutate(MatrixB_O_ingroup_points = case_when(
    MatrixB_O == "A" ~ 19,
    MatrixB_O == "B" ~ 18,
    MatrixB_O == "C" ~ 17,
    MatrixB_O == "D" ~ 16,
    MatrixB_O == "E" ~ 15,
    MatrixB_O == "F" ~ 14,
    MatrixB_O == "G" ~ 13,
    MatrixB_O == "H" ~ 12,
    MatrixB_O == "I" ~ 11,
    MatrixB_O == "J" ~ 10,
    MatrixB_O == "K" ~ 9,
    MatrixB_O == "L" ~ 8,
    MatrixB_O == "M" ~ 7
  )) %>%
  mutate(MatrixB_O_outgroup_points = case_when(
    MatrixB_O == "A" ~ 25,
    MatrixB_O == "B" ~ 23,
    MatrixB_O == "C" ~ 21,
    MatrixB_O == "D" ~ 19,
    MatrixB_O == "E" ~ 17,
    MatrixB_O == "F" ~ 15,
    MatrixB_O == "G" ~ 13,
    MatrixB_O == "H" ~ 11,
    MatrixB_O == "I" ~ 9,
    MatrixB_O == "J" ~ 7,
    MatrixB_O == "K" ~ 5,
    MatrixB_O == "L" ~ 3,
    MatrixB_O == "M" ~ 1
  ))


# Matrix 4: MD vs. MIP+MJP Together
groups2 <- groups2 %>%
  mutate(MatrixB_T_ingroup_points = case_when(
    MatrixB_T == "A" ~ 1,
    MatrixB_T == "B" ~ 3,
    MatrixB_T == "C" ~ 5,
    MatrixB_T == "D" ~ 7,
    MatrixB_T == "E" ~ 9,
    MatrixB_T == "F" ~ 11,
    MatrixB_T == "G" ~ 13,
    MatrixB_T == "H" ~ 15,
    MatrixB_T == "I" ~ 17,
    MatrixB_T == "J" ~ 19,
    MatrixB_T == "K" ~ 21,
    MatrixB_T == "L" ~ 23,
    MatrixB_T == "M" ~ 25
  )) %>%
  mutate(MatrixB_T_outgroup_points = case_when(
    MatrixB_T == "A" ~ 7,
    MatrixB_T == "B" ~ 8,
    MatrixB_T == "C" ~ 9,
    MatrixB_T == "D" ~ 10,
    MatrixB_T == "E" ~ 11,
    MatrixB_T == "F" ~ 12,
    MatrixB_T == "G" ~ 13,
    MatrixB_T == "H" ~ 14,
    MatrixB_T == "I" ~ 15,
    MatrixB_T == "J" ~ 16,
    MatrixB_T == "K" ~ 17,
    MatrixB_T == "L" ~ 18,
    MatrixB_T == "M" ~ 19
  ))


# Matrix 5: P Vs. FAV Opposed
groups2 <- groups2 %>%
  mutate(MatrixC_O_ingroup_points = case_when(
    MatrixC_O == "A" ~ 16,
    MatrixC_O == "B" ~ 17,
    MatrixC_O == "C" ~ 18,
    MatrixC_O == "D" ~ 19,
    MatrixC_O == "E" ~ 20,
    MatrixC_O == "F" ~ 21,
    MatrixC_O == "G" ~ 22,
    MatrixC_O == "H" ~ 23,
    MatrixC_O == "I" ~ 24,
    MatrixC_O == "J" ~ 25,
    MatrixC_O == "K" ~ 26,
    MatrixC_O == "L" ~ 27,
    MatrixC_O == "M" ~ 28
  )) %>%
  mutate(MatrixC_O_outgroup_points = case_when(
    MatrixC_O == "A" ~ 16,
    MatrixC_O == "B" ~ 15,
    MatrixC_O == "C" ~ 14,
    MatrixC_O == "D" ~ 13,
    MatrixC_O == "E" ~ 12,
    MatrixC_O == "F" ~ 11,
    MatrixC_O == "G" ~ 10,
    MatrixC_O == "H" ~ 9,
    MatrixC_O == "I" ~ 8,
    MatrixC_O == "J" ~ 7,
    MatrixC_O == "K" ~ 6,
    MatrixC_O == "L" ~ 5,
    MatrixC_O == "M" ~ 4
  ))


# Matrix 6: P Vs. FAV Together
groups2 <- groups2 %>%
  mutate(MatrixC_T_ingroup_points = case_when(
    MatrixC_T == "A" ~ 4,
    MatrixC_T == "B" ~ 5,
    MatrixC_T == "C" ~ 6,
    MatrixC_T == "D" ~ 7,
    MatrixC_T == "E" ~ 8,
    MatrixC_T == "F" ~ 9,
    MatrixC_T == "G" ~ 10,
    MatrixC_T == "H" ~ 11,
    MatrixC_T == "I" ~ 12,
    MatrixC_T == "J" ~ 13,
    MatrixC_T == "K" ~ 14,
    MatrixC_T == "L" ~ 15,
    MatrixC_T == "M" ~ 16
  )) %>%
  mutate(MatrixC_T_outgroup_points = case_when(
    MatrixC_T == "A" ~ 28,
    MatrixC_T == "B" ~ 27,
    MatrixC_T == "C" ~ 26,
    MatrixC_T == "D" ~ 25,
    MatrixC_T == "E" ~ 24,
    MatrixC_T == "F" ~ 23,
    MatrixC_T == "G" ~ 22,
    MatrixC_T == "H" ~ 21,
    MatrixC_T == "I" ~ 20,
    MatrixC_T == "J" ~ 19,
    MatrixC_T == "K" ~ 18,
    MatrixC_T == "L" ~ 17,
    MatrixC_T == "M" ~ 16
  ))
###################,
##CALCULATING PULLS
###################,
####Matrix A: Pull of FAV on MJP and Vice Versa
##Rankings for Opposed Matrix
MatrixA_O_Ranking<-dplyr::recode(groups2$MatrixA_O,'M' = 0,
                          'L' = 1,
                          'K' = 2,
                          'J' = 3,
                          'I' = 4,
                          'H' = 5,
                          'G' = 6,
                          'F' = 7,
                          'E' = 8,
                          'D' = 9,
                          'C' = 10,
                          'B' = 11,
                          'A' = 12)
##Ranking for Together Matrix
MatrixA_T_Ranking<-dplyr::recode(groups2$MatrixA_T,'M' = 12,
                          'L' = 11,
                          'K' = 10,
                          'J' = 9,
                          'I' = 8,
                          'H' = 7,
                          'G' = 6,
                          'F' = 5,
                          'E' = 4,
                          'D' = 3,
                          'C' = 2,
                          'B' = 1,
                          'A' = 0)
##Subtracting to Get Pulls
Pull_FAVonMJP<-MatrixA_O_Ranking-MatrixA_T_Ranking
Pull_MJPonFAV<-(12-MatrixA_O_Ranking)-MatrixA_T_Ranking

####Matrix B: Pull of MD on Profit and Vice Versa
##Ranking for Opposed Matrix
MatrixB_O_Ranking<-dplyr::recode(groups2$MatrixB_O,'M' = 12,
                          'L' = 11,
                          'K' = 10,
                          'J' = 9,
                          'I' = 8,
                          'H' = 7,
                          'G' = 6,
                          'F' = 5,
                          'E' = 4,
                          'D' = 3,
                          'C' = 2,
                          'B' = 1,
                          'A' = 0)

##Ranking for Together Matrix
MatrixB_T_Ranking<-dplyr::recode(groups2$MatrixB_T,'M' = 0,
                          'L' = 1,
                          'K' = 2,
                          'J' = 3,
                          'I' = 4,
                          'H' = 5,
                          'G' = 6,
                          'F' = 7,
                          'E' = 8,
                          'D' = 9,
                          'C' = 10,
                          'B' = 11,
                          'A' = 12)

##Subtracting to Get Pulls
Pull_MDonProfit<-MatrixB_O_Ranking-MatrixB_T_Ranking
Pull_ProfitonMD<-(12-MatrixB_O_Ranking)-MatrixB_T_Ranking

####Matrix C: Pull of P on FAV and Vice Versa
##Ranking for Opposed Matrix
MatrixC_O_Ranking<-dplyr::recode(groups2$MatrixC_O,'M' = 0,
                          'L' = 1,
                          'K' = 2,
                          'J' = 3,
                          'I' = 4,
                          'H' = 5,
                          'G' = 6,
                          'F' = 7,
                          'E' = 8,
                          'D' = 9,
                          'C' = 10,
                          'B' = 11,
                          'A' = 12)

##Ranking for Together Matrix
MatrixC_T_Ranking<-dplyr::recode(groups2$MatrixC_T,'M' = 12,
                          'L' = 11,
                          'K' = 10,
                          'J' = 9,
                          'I' = 8,
                          'H' = 7,
                          'G' = 6,
                          'F' = 5,
                          'E' = 4,
                          'D' = 3,
                          'C' = 2,
                          'B' = 1,
                          'A' = 0)

##Subtracting to Get Pulls
Pull_PonFAV<-MatrixC_O_Ranking-MatrixC_T_Ranking
Pull_FAVonP<-(12-MatrixC_O_Ranking)-MatrixC_T_Ranking


####Add Pulls to data
groups2$Pull_FAVonMJP<-Pull_FAVonMJP
groups2$Pull_MJPonFAV<-Pull_MJPonFAV

groups2$Pull_MDonProfit<-Pull_MDonProfit
groups2$Pull_ProfitonMD<-Pull_ProfitonMD

groups2$Pull_PonFAV<-Pull_PonFAV
groups2$Pull_FAVonP<-Pull_FAVonP


# calculate the total number of ingroup points and total number of outgroup points.
groups2 <- groups2 %>%
  rowwise() %>%
  mutate(total_ingroup_points = sum(c(MatrixA_O_ingroup_points,MatrixA_T_ingroup_points,
                                      MatrixB_O_ingroup_points,MatrixB_T_ingroup_points,
                                      MatrixC_O_ingroup_points,MatrixC_T_ingroup_points), na.rm = T)) %>%
  mutate(total_outgroup_points = sum(c(MatrixA_O_outgroup_points,MatrixA_T_outgroup_points,
                                      MatrixB_O_outgroup_points,MatrixB_T_outgroup_points,
                                      MatrixC_O_outgroup_points,MatrixC_T_outgroup_points), na.rm = T)) %>%
  ungroup()


# calculate the difference between the total number of points awarded to the ingroup and the total outgroup points awarded to outgroup.
groups2 <- groups2 %>%
  mutate(total_ingroup_minus_outgroup_points = total_ingroup_points - total_outgroup_points,
         z_total_ingroup_minus_outgroup_points = scale(total_ingroup_minus_outgroup_points))

```

## SCORE MEDIATORS

```{r}
## MORAL FOUNDATIONS QUESTIONNAIRE
#Part 1
groups2$mf_pt1_1 <- dplyr::recode(groups2$mf_pt1_1, 
                         "Not at all Relevant" = 1,
                         "Not very Relevant" = 2,
                         "Slightly Relevant" = 3,
                         "Somewhat Relevant" = 4,
                         "Very Relevant" = 5,
                         "Extremely Relevant" = 6)

groups2$mf_pt1_2 <- dplyr::recode(groups2$mf_pt1_2, 
                         "Not at all Relevant" = 1,
                         "Not very Relevant" = 2,
                         "Slightly Relevant" = 3,
                         "Somewhat Relevant" = 4,
                         "Very Relevant" = 5,
                         "Extremely Relevant" = 6)

groups2$mf_pt1_3 <- dplyr::recode(groups2$mf_pt1_3, 
                         "Not at all Relevant" = 1,
                         "Not very Relevant" = 2,
                         "Slightly Relevant" = 3,
                         "Somewhat Relevant" = 4,
                         "Very Relevant" = 5,
                         "Extremely Relevant" = 6)

groups2$mf_pt1_4 <- dplyr::recode(groups2$mf_pt1_4, 
                         "Not at all Relevant" = 1,
                         "Not very Relevant" = 2,
                         "Slightly Relevant" = 3,
                         "Somewhat Relevant" = 4,
                         "Very Relevant" = 5,
                         "Extremely Relevant" = 6)

groups2$mf_pt1_5 <- dplyr::recode(groups2$mf_pt1_5, 
                         "Not at all Relevant" = 1,
                         "Not very Relevant" = 2,
                         "Slightly Relevant" = 3,
                         "Somewhat Relevant" = 4,
                         "Very Relevant" = 5,
                         "Extremely Relevant" = 6)

groups2$mf_pt1_6 <- dplyr::recode(groups2$mf_pt1_6, 
                         "Not at all Relevant" = 1,
                         "Not very Relevant" = 2,
                         "Slightly Relevant" = 3,
                         "Somewhat Relevant" = 4,
                         "Very Relevant" = 5,
                         "Extremely Relevant" = 6)

groups2$mf_pt1_7 <- dplyr::recode(groups2$mf_pt1_7, 
                         "Not at all Relevant" = 1,
                         "Not very Relevant" = 2,
                         "Slightly Relevant" = 3,
                         "Somewhat Relevant" = 4,
                         "Very Relevant" = 5,
                         "Extremely Relevant" = 6)

groups2$mf_pt1_8 <- dplyr::recode(groups2$mf_pt1_8, 
                         "Not at all Relevant" = 1,
                         "Not very Relevant" = 2,
                         "Slightly Relevant" = 3,
                         "Somewhat Relevant" = 4,
                         "Very Relevant" = 5,
                         "Extremely Relevant" = 6)

groups2$mf_pt1_9 <- dplyr::recode(groups2$mf_pt1_9, 
                         "Not at all Relevant" = 1,
                         "Not very Relevant" = 2,
                         "Slightly Relevant" = 3,
                         "Somewhat Relevant" = 4,
                         "Very Relevant" = 5,
                         "Extremely Relevant" = 6)

#Part 2
groups2$mf_pt2_1 <- dplyr::recode(groups2$mf_pt2_1, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$mf_pt2_2 <- dplyr::recode(groups2$mf_pt2_2, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$mf_pt2_3 <- dplyr::recode(groups2$mf_pt2_3, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$mf_pt2_4 <- dplyr::recode(groups2$mf_pt2_4, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$mf_pt2_5 <- dplyr::recode(groups2$mf_pt2_5, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$mf_pt2_6 <- dplyr::recode(groups2$mf_pt2_6, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$mf_pt2_7 <- dplyr::recode(groups2$mf_pt2_7, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$mf_pt2_8 <- dplyr::recode(groups2$mf_pt2_8, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$mf_pt2_9 <- dplyr::recode(groups2$mf_pt2_9, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)
groups2 %<>% 
  rowwise() %>% 
  mutate(mf1_score = mean(c(mf_pt1_1, mf_pt1_2, mf_pt1_3, mf_pt1_4, mf_pt1_5,
                          mf_pt1_6, mf_pt1_7, mf_pt1_8, mf_pt1_9)),
         mf2_score = mean(c(mf_pt2_1, mf_pt2_2, mf_pt2_3, mf_pt2_4, mf_pt2_5,
                          mf_pt2_6, mf_pt2_7, mf_pt2_8, mf_pt2_9)),
         mf_composite = mean(c(mf_pt1_1, mf_pt1_2, mf_pt1_3, mf_pt1_4, mf_pt1_5,
                          mf_pt1_6, mf_pt1_7, mf_pt1_8, mf_pt1_9,mf_pt2_1, mf_pt2_2,                            mf_pt2_3, mf_pt2_4, mf_pt2_5,
                          mf_pt2_6, mf_pt2_7, mf_pt2_8, mf_pt2_9))) %>% 
  ungroup() %>% 
  mutate(mf1_z = scale(mf1_score),
         mf2_z = scale(mf2_score),
         mf_z  = scale(mf_composite))


## NEED FOR CLOSURE SCALE
groups2$NFCC_1<-dplyr::recode(groups2$NFCC_1, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$NFCC_2<-dplyr::recode(groups2$NFCC_2, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$NFCC_3<-dplyr::recode(groups2$NFCC_3, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)
groups2$NFCC_4 <- dplyr::recode(groups2$NFCC_4, 
                        "Strongly Disagree" = 1,
                        "Moderately Disagree" = 2,
                        "Slightly Disagree" = 3,
                        "Slightly Agree" = 4,
                        "Moderately Agree" = 5,
                        "Strongly Agree" = 6)

groups2$NFCC_5 <- dplyr::recode(groups2$NFCC_5, 
                        "Strongly Disagree" = 1,
                        "Moderately Disagree" = 2,
                        "Slightly Disagree" = 3,
                        "Slightly Agree" = 4,
                        "Moderately Agree" = 5,
                        "Strongly Agree" = 6)

groups2$NFCC_6 <- dplyr::recode(groups2$NFCC_6, 
                        "Strongly Disagree" = 1,
                        "Moderately Disagree" = 2,
                        "Slightly Disagree" = 3,
                        "Slightly Agree" = 4,
                        "Moderately Agree" = 5,
                        "Strongly Agree" = 6)

groups2$NFCC_7 <- dplyr::recode(groups2$NFCC_7, 
                        "Strongly Disagree" = 1,
                        "Moderately Disagree" = 2,
                        "Slightly Disagree" = 3,
                        "Slightly Agree" = 4,
                        "Moderately Agree" = 5,
                        "Strongly Agree" = 6)

groups2$NFCC_8 <- dplyr::recode(groups2$NFCC_8, 
                        "Strongly Disagree" = 1,
                        "Moderately Disagree" = 2,
                        "Slightly Disagree" = 3,
                        "Slightly Agree" = 4,
                        "Moderately Agree" = 5,
                        "Strongly Agree" = 6)

groups2$NFCC_9 <- dplyr::recode(groups2$NFCC_9, 
                        "Strongly Disagree" = 1,
                        "Moderately Disagree" = 2,
                        "Slightly Disagree" = 3,
                        "Slightly Agree" = 4,
                        "Moderately Agree" = 5,
                        "Strongly Agree" = 6)

groups2$NFCC_10 <- dplyr::recode(groups2$NFCC_10, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$NFCC_11 <- dplyr::recode(groups2$NFCC_11, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$NFCC_12 <- dplyr::recode(groups2$NFCC_12, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$NFCC_13 <- dplyr::recode(groups2$NFCC_13, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$NFCC_14 <- dplyr::recode(groups2$NFCC_14, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2$NFCC_15 <- dplyr::recode(groups2$NFCC_15, 
                         "Strongly Disagree" = 1,
                         "Moderately Disagree" = 2,
                         "Slightly Disagree" = 3,
                         "Slightly Agree" = 4,
                         "Moderately Agree" = 5,
                         "Strongly Agree" = 6)

groups2 %<>% 
  rowwise() %>% 
  mutate(closure = mean(c(NFCC_1, NFCC_2, NFCC_3, NFCC_4, NFCC_5,
                          NFCC_6, NFCC_7, NFCC_8, NFCC_9, NFCC_10,
                          NFCC_11, NFCC_12, NFCC_13, NFCC_14, NFCC_15))) %>% 
  ungroup() %>% 
  mutate(closure_z = scale(closure))


##SOCIAL NORMS
groups2$norms_amer_accept<-dplyr::recode(groups2$norms_amer_accept, 
                         "Not at all 1" = 1,
                         "2" = 2,
                         "3" = 3,
                         "4" = 4,
                         "5" = 5,
                         "6" = 6,
                         "Very much 7" = 7)

groups2$norms_amer_express<-dplyr::recode(groups2$norms_amer_express, 
                         "Not at all 1" = 1,
                         "2" = 2,
                         "3" = 3,
                         "4" = 4,
                         "5" = 5,
                         "6" = 6,
                         "Very much 7" = 7)

groups2$norms_admire_accept<-dplyr::recode(groups2$norms_admire_accept, 
                         "Not at all 1" = 1,
                         "2" = 2,
                         "3" = 3,
                         "4" = 4,
                         "5" = 5,
                         "6" = 6,
                         "Very much 7" = 7)


groups2$norms_admire_express<-dplyr::recode(groups2$norms_admire_express, 
                         "Not at all 1" = 1,
                         "2" = 2,
                         "3" = 3,
                         "4" = 4,
                         "5" = 5,
                         "6" = 6,
                         "Very much 7" = 7)

groups2 <- groups2 %>% 
  mutate(norms_amer_accept_z = scale(norms_amer_accept),
         norms_amer_express_z = scale(norms_amer_express),
         norms_admire_accept_z = scale(norms_admire_accept),
         norms_admire_express_z = scale(norms_admire_express))

groups2 %<>% 
  rowwise() %>% 
  mutate(social_norms = mean(c(norms_amer_accept, norms_amer_express, norms_admire_accept, norms_admire_express))) %>% 
  ungroup() %>% 
  mutate(social_norms_z = scale(social_norms))

```


############################################,
## CREATE COMPOSITE INTERGROUP BIAS MEASURE.
############################################,
```{r}

# calculate mean intergroup bias using the three standardized measures.
groups2 <- groups2 %>%
  rowwise() %>%
  mutate(mean_intergroup_bias = mean(c(z_total_ingroup_minus_outgroup_points,z_ingroup_minus_outgroup_traits_positive,z_ingroup_minus_outgroup_identify))) %>%
  ungroup() %>% 
  mutate(mean_intergroup_bias_z = scale(mean_intergroup_bias))


########################################################################,
## CREATE SEPARTE INGROUP/OUTGROUP INDICES OF INTERGROUP BIAS MEASURE.##
########################################################################,
##Ingroup Index 
#within sample
groups2 <- groups2 %>%
  mutate(z_IngroupIdentify = scale(IngroupIdentify),
         z_IngroupTraits   = scale(mean_ingroup_traits_positive),
         z_IngroupPoints   = scale(total_ingroup_points)) %>%
  ungroup()

groups2 <- groups2 %>% 
  rowwise() %>% 
  mutate(IngroupIndex=mean(c(z_IngroupIdentify,z_IngroupTraits,z_IngroupPoints))) %>% 
  ungroup() %>% 
  mutate(IngroupIndex_z = scale(IngroupIndex))


##Outgroup Index 
groups2 <- groups2 %>%
  mutate(z_OutgroupIdentify = scale(OutgroupIdentify),
         z_OutgroupTraits   = scale(mean_outgroup_traits_positive),
         z_OutgroupPoints   = scale(total_outgroup_points)) %>%
  ungroup()

groups2 <- groups2 %>% 
  rowwise() %>% 
  mutate(OutgroupIndex = mean(c(z_OutgroupIdentify,z_OutgroupTraits,z_OutgroupPoints))) %>% 
  ungroup() %>% 
  mutate(OutgroupIndex_z = scale(OutgroupIndex))

write.csv(groups2, "/Users/youssefamin/Dropbox/MinimalGroup_NHB_Master/MinimalGroup_NHB2/data/nhb2_processed.csv")

```

```{r run all before, echo=FALSE}

```