---
title: "NHB2 - Confirmatory Analyses"
author: "Youssef Amin and Angelika Stefan"
date: "2024-06-05"
output: html_document
---
## Load packages
```{r setup, message=FALSE, warning=FALSE, error = FALSE}
library(bayestestR)
library(ggplot2)
library(brms)
library(logspline)
library(emmeans)
```
  
<br>
<br> 

## Read in data
```{r read in data}
# Set seed
set.seed (987654)
nhb3 <- read.csv("../../data/nhb3_processed.csv")
nhb3$condition <- factor(nhb3$condition, 
                         levels = c("no_interaction", "cooperative", "competitive"),
                         labels = c("No_Interaction", "Cooperative", "Competitive"))
```
  
  
  
<br>
<br>
<br>

# Confirmatory Analyses

## Summary
1. <span style="color:green">Ideology</span> predicts <span style="color:green">intergroup bias</span>. 
2. <span style="color:red">Group type</span> does <span style ="color:red">not</span> moderate the relationship between <span style="color:red">ideology</span> and <span style="color:red">bias</span>. There is a main effect of the <span style="color:green">Competitive</span> condition.
  
  
  
  
<br>
<br>

## Confirmatory 1: <span style="color:green">Ideology</span> predicts <span style="color:green">bias</span>
```{r confirmatory 1 formula}
confirmatory1_formula <- mean_intergroup_bias_z ~ composite_political_orientation_z
```
<br> 

### Compute Frequentist
```{r confirmatory 1 compute frequentist}
confirmatory1_freqmodel <- lm(confirmatory1_formula, nhb3)
df_confirm1 <- confirmatory1_freqmodel$df.residual
t_confirm1 <- summary(confirmatory1_freqmodel)$coefficients[2,]["t value"]
p_confirm1 <- 1-pt(t_confirm1, df_confirm1)
```
<br>

### Compute Bayesian: Default Priors
```{r confirmatory 1 compute bayesian default, results = 'hide', warning=FALSE, message=FALSE }
### Define priors for the regression model #REMEMBER TO SET warmup = 5000 and iter = 100000
confirmatory1_DefaultPriors <- c(set_prior("normal(0, 0.5)", class = "b"))

# Run the regression model
confirmatory1_bayesmodel_default <- brm(
  formula = confirmatory1_formula, 
  data = nhb3, 
  family = gaussian(),
  prior = confirmatory1_DefaultPriors,
  sample_prior = "no",
  iter = 100000,  # Adjust iterations based on convergence diagnostics
  chains = 4,
  seed = 987654,
  silent = TRUE,
  refresh = 0,
  warmup = 5000
)

confirmatory1_priordraws_default<- brms::brm(confirmatory1_formula, 
                            data = nhb3, 
                            family = "gaussian",
                            prior = confirmatory1_DefaultPriors,
                            sample_prior = "only",
                            seed = 987654,
                            silent = TRUE,
                            refresh = 0,
                            iter = 100000)

confirmatory1_bf_default <- bayesfactor_parameters(confirmatory1_bayesmodel_default,
                       prior=confirmatory1_priordraws_default, 
                       direction = "right", 
                       parameters = "composite_political_orientation_z")
```

<br>
<br>

### Compute Bayesian: Informed Priors
```{r confirmatory 1 compute bayesian informed, results = 'hide', warning=FALSE, message=FALSE }
### Define priors for the regression model #REMEMBER TO SET warmup = 5000 and iter = 100000
confirmatory1_InformedPriors <- c(set_prior("normal(0.15, 0.05)", class = "b"))

# Run the regression model
confirmatory1_bayesmodel_informed <- brm(
  formula = confirmatory1_formula, 
  data = nhb3, 
  family = gaussian(),
  prior = confirmatory1_InformedPriors,
  sample_prior = "no",
  iter = 100000,  # Adjust iterations based on convergence diagnostics
  chains = 4,
  seed = 987654,
  silent = TRUE,
  refresh = 0,
  warmup = 5000
)

confirmatory1_priordraws_informed<- brms::brm(confirmatory1_formula, 
                            data = nhb3, 
                            family = "gaussian",
                            prior = confirmatory1_InformedPriors,
                            sample_prior = "only",
                            seed = 987654,
                            silent = TRUE,
                            refresh = 0,
                            iter = 100000)

confirmatory1_bf_informed <- bayesfactor_parameters(confirmatory1_bayesmodel_informed,
                       prior=confirmatory1_priordraws_informed, 
                       direction = "right", 
                       parameters = "composite_political_orientation_z")
```


```{r confirmatory 1 plot, results='hide', echo=FALSE, warning=FALSE, message=FALSE}
confirmatory1_bf_long <- round(exp(confirmatory1_bf_default$log_BF), 3)
confirmatory1_beta <- round(confirmatory1_bayesmodel_default[["fit"]]@.MISC[["summary"]]$msd["b_composite_political_orientation_z", "mean"],2)
confirmatory1_plot <- ggplot(nhb3, aes(x = composite_political_orientation_z, y = mean_intergroup_bias_z, 
                                       color = composite_political_orientation_z)) +
  geom_point(size = 3, alpha = 0.7) +
  geom_smooth(method = "lm", color = "black", linetype = "solid") +
  scale_color_gradient2(low = "darkblue", mid = "darkgrey", high = "red", midpoint = 0) +
  labs(
    x = "Ideology (z-scored)",
    y = "Minimal Intergroup Bias (z-scored)",
    title = "Relationship between Ideology and Minimal Intergroup Bias",
    color = "Ideology"
  ) +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, 
           label = 
             bquote(beta[z] == .(paste(confirmatory1_beta, ",", sep =''))~
                      'BF'[10] == .(formatC(log10(confirmatory1_bf_long), format = "fg", digits = 3)) %*% 10^.(floor(log10(confirmatory1_bf_long)))),
           parse = FALSE,
           hjust = 1.1, vjust = 1.1, size = 5, color = "black") +
  theme(plot.title = element_text(hjust = 0.5))
  confirmatory1_plot
```
  
### Confirmatory 1 Results: <span style="color:green">Ideology</span> predicts <span style="color:green">intergroup bias</span>. 
```{r confirmatory 1 results}
###FREQUENTIST
summary(confirmatory1_freqmodel)
print(paste0("Confirmatory 1 p value is ", p_confirm1))
confint(confirmatory1_freqmodel)

###BAYESIAN
##Default
summary(confirmatory1_bayesmodel_default)
confirmatory1_bf_default

###Informed
summary(confirmatory1_bayesmodel_informed)
confirmatory1_bf_informed
```
<br>
<br>

## Confirmatory 2: <span style="color:red">Group type</span> does **not** moderate relationship between <span style="color:red">ideology</span> and <span style="color:red">bias</span>. There is a main effect of the <span style="color:green">Competitive</span> condition.
```{r confirmatory 2 formula}
confirmatory2_formula <- mean_intergroup_bias_z ~ composite_political_orientation_z + condition + composite_political_orientation_z:condition
```
<br>






### Compute Frequentist
```{r confirmatory 2 compute frequentist}
confirmatory2_freqmodel <- lm(confirmatory2_formula, data = nhb3)
df_confirm2 <- confirmatory2_freqmodel$df.residual

t_random <- summary(confirmatory2_freqmodel)$coefficients["composite_political_orientation_z", "t value"]

t_Cooperative_interaction <- summary(confirmatory2_freqmodel)$coefficients["composite_political_orientation_z:conditionCooperative", "t value"]

t_Competitive_interaction <- summary(confirmatory2_freqmodel)$coefficients["composite_political_orientation_z:conditionCompetitive", "t value"]

t_Cooperative_maineffect<- summary(confirmatory2_freqmodel)$coefficients["conditionCooperative", "t value"]

t_Competitive_maineffect <- summary(confirmatory2_freqmodel)$coefficients["conditionCompetitive", "t value"]

# Compute one-sided p-values

p_random <- 1-pt(t_random, df_confirm2)

p_Cooperative_maineffect <- 1-pt(t_Cooperative_maineffect, df_confirm2)
p_Competitive_maineffect <- 1-pt(t_Competitive_maineffect, df_confirm2)

p_Cooperative_interaction <- 1-pt(t_Cooperative_interaction, df_confirm2)
p_Competitive_interaction <- 1-pt(t_Competitive_interaction, df_confirm2)

```

<br>





### Compute Bayesian: Default Priors
```{r confirmatory 2 compute bayesian default, results = 'hide', warning=FALSE, message=FALSE }
priors_list <- get_prior(
  formula = confirmatory2_formula,
  data = nhb3,
  family = gaussian()
)
priors_list$coef #use this to get the names of the variables/their format you need to input into modelprios


confirmatory2_DefaultPriors <- c(
  set_prior("normal(0, 0.5)", class = "b", coef="composite_political_orientation_z"),
  set_prior("normal(0, 0.5)", class = "b", coef="conditionCompetitive"),
  set_prior("normal(0, 0.5)", class = "b", coef="conditionCooperative"),
  
  set_prior("normal(0, 0.2)", class = "b", coef="composite_political_orientation_z:conditionCompetitive"),
  set_prior("normal(0, 0.2)", class = "b", coef="composite_political_orientation_z:conditionCooperative")
)

confirmatory2_bayesmodel_default <- brms::brm(
  formula = confirmatory2_formula, 
                  data = nhb3, 
                  family = "gaussian",
                  prior = confirmatory2_DefaultPriors,
                  sample_prior = "no",
                  iter = 100000,
                  warmup = 5000,
                  chains = 4,
                  seed = 987654)

confirmatory2_priordraws_default <- brms::brm(confirmatory2_formula, 
                        data = nhb3, 
                        family = "gaussian",
                        prior = confirmatory2_DefaultPriors,
                        sample_prior = "only",
                        iter = 100000,
                        seed = 987654)

confirmatory2_bf_default <- bayesfactor_parameters(confirmatory2_bayesmodel_default,
                       prior=confirmatory2_priordraws_default,
                       direction = "right")

```
<br>

### Compute Bayesian: Informed Priors
```{r confirmatory 2 compute bayesian informed, results = 'hide', warning=FALSE, message=FALSE }
priors_list <- get_prior(
  formula = confirmatory2_formula,
  data = nhb3,
  family = gaussian()
)
priors_list$coef #use this to get the names of the variables/their format you need to input into modelprios


confirmatory2_InformedPriors <- c(
  set_prior("normal(0.15, 0.05)", class = "b", coef="composite_political_orientation_z"),
  set_prior("normal(0.1, 0.5)", class = "b", coef="conditionCompetitive"),
  set_prior("normal(0.1, 0.5)", class = "b", coef="conditionCooperative"),
  
  set_prior("normal(0.1, 0.05)", class = "b", coef="composite_political_orientation_z:conditionCompetitive"),
  set_prior("normal(0.1, 0.05)", class = "b", coef="composite_political_orientation_z:conditionCooperative")
)

confirmatory2_bayesmodel_informed <- brms::brm(
  formula = confirmatory2_formula, 
                  data = nhb3, 
                  family = "gaussian",
                  prior = confirmatory2_InformedPriors,
                  sample_prior = "no",
                  iter = 100000,
                  warmup = 5000,
                  chains = 4,
                  seed = 987654)

confirmatory2_priordraws_informed <- brms::brm(confirmatory2_formula, 
                        data = nhb3, 
                        family = "gaussian",
                        prior = confirmatory2_InformedPriors,
                        sample_prior = "only",
                        iter = 100000,
                        seed = 987654)

confirmatory2_bf_informed <- bayesfactor_parameters(confirmatory2_bayesmodel_informed,
                       prior=confirmatory2_priordraws_informed,
                       direction = "right")

```


<br>

```{r confirmatory 2 plot, echo = FALSE, results='hide', warning=FALSE, message=FALSE}
posterior <- as_draws_df(confirmatory2_bayesmodel_default)
beta_random <- mean(posterior$b_composite_political_orientation_z)
beta_Cooperative <- mean(posterior$`b_composite_political_orientation_z:conditionCooperative`) + beta_random
beta_Competitive <- mean(posterior$`b_composite_political_orientation_z:conditionCompetitive`) + beta_random

beta_values <- data.frame(
  condition = c("No_Interaction", "Cooperative", "Competitive"),
  beta = c(beta_random, beta_Cooperative, beta_Competitive),
  betalabel = paste0("β[z] == ", round(c(beta_random, beta_Cooperative, beta_Competitive), 2))
)



ggplot(nhb3, aes(x = composite_political_orientation_z, 
                 y = mean_intergroup_bias_z, 
                 color = composite_political_orientation_z)) +
  geom_point(alpha = 0.5, size = 1.5) +  # Scatter points
  geom_smooth(method = "lm", color = "black") +  # Regression lines
  scale_color_gradient2(low = "darkblue", mid = "darkgray", high = "red", midpoint = 0) +  # Color gradient
  facet_wrap(~factor(condition, levels =c("No_Interaction", "Cooperative", "Competitive")), nrow = 1) +  # Facet by condition
  theme_minimal() +
  labs(
    title = "Group Condition as Moderator",
    x = "Ideology (z-scored)",
    y = "Minimal Intergroup Bias (z-scored)",
    color = "Ideology"
  ) +
  geom_text(data = beta_values, 
            mapping = aes(x = 0, y = 3.5, label = betalabel),
            color = "black", parse = TRUE, inherit.aes = FALSE)

```

### Confirmatory 2 Results: <span style="color:red">Group type</span> did <span style ="color:red">not</span> moderate relationship between <span style="color:red">ideology</span> and <span style="color:red">bias</span>. There is a main effect of the <span style="color:green">Competitive</span> condition.


```{r confirmatory 2 results}
###FREQUENTIST
summary(confirmatory2_freqmodel)
confint(confirmatory2_freqmodel)
print(paste0("Confirmatory 2 (Cooperative main effect) p value is ", p_Cooperative_maineffect))
print(paste0("Confirmatory 2 (Competitive main effect) p value is ", p_Competitive_maineffect))

print(paste0("Confirmatory 2 (Cooperative interaction effect) p value is ", p_Cooperative_interaction))
print(paste0("Confirmatory 2 (Competitive interaction effect) p value is ", p_Competitive_interaction))

##Simple Slopes (one-sided p-values)
simpleslopes_freq <- test(emtrends(confirmatory2_freqmodel, "condition", var = "composite_political_orientation_z"))
cbind(condition = as.character(simpleslopes_freq$condition),
      pvalue_onesided=1-pt(simpleslopes_freq$t.ratio, df=simpleslopes_freq$df))

###BAYESIAN
##Default
summary(confirmatory2_bayesmodel_default)
confirmatory2_bf_default

##Simple Slopes - Calculation of point estimates and CIs
hypothesis(confirmatory2_bayesmodel_default, c("composite_political_orientation_z = 0", 
                                       "composite_political_orientation_z + composite_political_orientation_z:conditionCooperative = 0", 
                                       "composite_political_orientation_z + composite_political_orientation_z:conditionCompetitive = 0"))

## Simple Slopes - Calculation of one-sided Bayes factors (BF+0)
simpleslopes_bayes <- emtrends(confirmatory2_bayesmodel_default, "condition", var="composite_political_orientation_z")
simpleslopes_bayes0 <- emtrends(confirmatory2_priordraws_default, "condition", var="composite_political_orientation_z")
bayesfactor_parameters(simpleslopes_bayes, prior = simpleslopes_bayes0, direction = "right")

##Informed
summary(confirmatory2_bayesmodel_informed)
confirmatory2_bf_informed

##Simple Slopes - Calculation of point estimates and CIs
hypothesis(confirmatory2_bayesmodel_informed, c("composite_political_orientation_z = 0", 
                                       "composite_political_orientation_z + composite_political_orientation_z:conditionCooperative = 0", 
                                       "composite_political_orientation_z + composite_political_orientation_z:conditionCompetitive = 0"))

## Simple Slopes - Calculation of one-sided Bayes factors (BF+0)
simpleslopes_bayes_inf <- emtrends(confirmatory2_bayesmodel_informed, "condition", var="composite_political_orientation_z")
simpleslopes_bayes0_inf <- emtrends(confirmatory2_priordraws_informed, "condition", var="composite_political_orientation_z")
bayesfactor_parameters(simpleslopes_bayes_inf, prior = simpleslopes_bayes0_inf, direction = "right")

```
